%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Classicthesis-Styled CV
% LaTeX Template
% Version 1.0 (22/2/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Alessandro Plasmati
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{scrartcl}

\reversemarginpar % Move the margin to the left of the page 

\newcommand{\MarginText}[1]{\marginpar{\raggedleft\itshape\small#1}} % New command defining the margin text style

\usepackage[nochapters]{classicthesis} % Use the classicthesis style for the style of the document
\usepackage[LabelsAligned]{currvita} % Use the currvita style for the layout of the document

\renewcommand{\cvheadingfont}{\LARGE\color{Maroon}} % Font color of your name at the top

\usepackage{hyperref} % Required for adding links	and customizing them
\hypersetup{colorlinks, breaklinks, urlcolor=Maroon, linkcolor=Maroon} % Set link colors

\newlength{\datebox}\settowidth{\datebox}{Spring 2011} % Set the width of the date box in each block

\newcommand{\NewEntry}[3]{\noindent\hangindent=2em\hangafter=0 \parbox{\datebox}{\small \textit{#1}}\hspace{1.5em} #2 #3 % Define a command for each new block - change spacing and font sizes here: #1 is the left margin, #2 is the italic date field and #3 is the position/employer/location field
\vspace{0.5em}} % Add some white space after each new entry

\newcommand{\Description}[1]{\hangindent=2em\hangafter=0\noindent\raggedright\footnotesize{#1}\par\normalsize\vspace{1em}} % Define a command for descriptions of each entry - change spacing and font sizes here

%----------------------------------------------------------------------------------------

\begin{document}

\thispagestyle{empty} % Stop the page count at the bottom of the first page

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\begin{cv}{\spacedallcaps{Matthew J. Kirk}}\vspace{1.5em} % Your name

\noindent\spacedlowsmallcaps{Personal Information}\vspace{0.5em} % Personal information heading

\NewEntry{}{\textit{Born in United States,}}{18 March 1987} % Birthplace and date

\NewEntry{email}{\href{mailto:matt@matthewkirk.com}{matt@matthewkirk.com}} % Email address

\NewEntry{website}{\href{http://www.matthewkirk.com}{http://www.matthewkirk.com}} % Personal website

\NewEntry{phone}{(W) +1 (206) 659 8072\ \ $\cdotp$\ \ (M) +1 (206) 409 6413} % Phone number(s)

\NewEntry{twitter}{\href{http://www.twitter.com/mjkirk}{@mjkirk}} % Twitter Handle

\NewEntry{github}{\href{http://www.github.com/hexgnu}{@hexgnu}} % Github Handle

\vspace{1em} % Extra white space between the personal information section and goal

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE
%----------------------------------------------------------------------------------------

\noindent\spacedlowsmallcaps{Work Experience}\vspace{1em}

\NewEntry{2009--Present}{Partner, \textsc{Modulus 7}}

\Description{
  \MarginText{Modulus 7}
Modulus 7 is a consultancy devoted to helping medium sized startups realize their potential through data analysis and engineering. We have had many clients since 2009 including but not limited to:

\begin{itemize}
  \item \href{http://www.siren.mobi}{Siren}
    Siren is a progressive dating application that seeks to protect women from being approached too aggressively. While working with Siren we refactored an existing app written in Objective-C and Rails to end up winning best app of the year from Geekwire. In addition gave advice on how to analyze their data related with dating. \newline
    Reference: Katrina \textsc{Hess}\ \ $\cdotp$\ \ \href{mailto:katrinahess@gmail.com}{katrinahess@gmail.com}
  \item \href{http://www.ritani.com}{Ritani}
    Ritani is a diamond company similar to BlueNile.com. While working with Ritani I have helped invent a strategy for recommending diamonds using common diamond features as well as build a scalable site that handles millions of pageviews per month. \newline
    Reference: Simon \textsc{Tam}\ \ $\cdotp$\ \ \href{mailto:simont@ritani.com}{simont@ritani.com}
  \item \href{http://www.theclymb.com}{The Clymb}
    Before becoming a full time data scientist at The Clymb I built the first version of their search capability using Elasticsearch. Also provided brand affinity analysis using Markov Chains. \newline
    Reference: Lorenzo \textsc{Ciacci}\ \ $\cdotp$\ \href{mailto:lono@houseofyeti.com}{lono@houseofyeti.com}
  \item \href{http://www.sqoop.com}{Sqoop}
    Sqoop is an app that seeks to deliver relevant news to journalists and is already used by GeekWire and Motley Fool. \newline
    Reference: Bill \textsc{Hankes}\ \ $\cdotp$\ \href{mailto:bill@sqoop.com}{bill@sqoop.com}
\end{itemize}}

\NewEntry{2014-2015}{Data Scientist, \textsc{The Clymb}}

\Description{\MarginText{The Clymb}
Lead new initiatives to bring data driven statistics to marketing and customer support. Reduced spending substantially through paying down technical debt.
\begin{itemize}
  \item Refactored and deployed a new scalable data warehouse using MySQL
  \item Built custom clickstream analysis tool, which lead to valuable insights about customer behaviors.
  \item Reduced server cost per month by revamping data infrastructure using Chef and Vagrant.
  \item Analyzed complex data using \textsc{R}, \textsc{Python}, and \textsc{SQL}
  \item Refactored and managed over 10,000 lines of \textsc{SQL} code.
\end{itemize}

 Reference: Mike \textsc{Perham}\ \ $\cdotp$\ \ \href{mailto:mperham@gmail.com}{mperham@gmail.com}
}

\NewEntry{2011-2012}{Chief Scientist, \textsc{SocialVolt}}

\Description{\MarginText{SocialVolt} Lead team of four developers producing an enterprise brand management tool. Campaign to pay technical debt and reduce total software defects.

\begin{itemize}
  \item Developed clustering algorithm that utilizes a multi dimensional hash and binary trees. Will deliver clusters extremely fast.
  \item Implemented sentiment analysis and spam filtering for large amounts of social media posts.
  \item Improved SocialVolt's development process by introducing design patterns and refactoring legacy code base.
  \item Managed team to build proof of concept to determine influential individuals on Twitter and Facebook
\end{itemize}

Reference: Scott \textsc{Oppliger}\ \ $\cdotp$\ \ \href{mailto:scott@socialvolt.com}{scott@socialvolt.com}}

\NewEntry{2009-2011}{Software Engineer II, \textsc{Wetpaint}}

\Description{\MarginText{Wetpaint} Provide a broad range of expertise, from architecting software to making reccomendations on critical technology decisions, web strategy and business development. Serve as the team's "Ruby Expert."

\begin{itemize}
  \item Lead project to develop what became the "Social Distribution System". This system was an expert system that would detect features related with success on editorial articles on Facebook. Involved extensive natural language processing and feature detection.
\item Lead all "Rails" development, including leveraging Ruby and Alfresco to build a framework for a network of entertainment sites.
\item Partnered in managing a large, technically complex transition. Shifted Wetpaint's focus from a user-generated content business to an editorial content business. Prototyped platform decisions using Ruby and Sinatra.
\item Built wetpaint.com which has achieved over 10MM+ monthly unique visitors.
\end{itemize}

Reference: Rob \textsc{Grady}\ \ $\cdotp$\ \ \href{mailto:rgrady@gmail.com}{rgrady@gmail.com}}

\NewEntry{2008-2009}{Assistant Research Analyst, \textsc{Parametric}}

\Description{ \MarginText{Parametric Portfolio Associates} Delivered objective research for high net-worth clients. Developed enterprise software and researched program development opportunities. \begin{itemize}
\item Partnered in developing an enhanced income portfolio product, which now has over \$80MM in managed assets. collaborated on development of a quantitative international portfolio strategy
\item Improved Eaton Vance's Structured Emerging Markets portfolio which now has over \$11B in assets under management. 
\item Wrote original research, which became the Russell CrossVol Index
\item Designed a web-based tool in C\# to provide portfolio managers with market volatility reports.
\end{itemize}

Reference: Paul \textsc{Bouchey}\ \ $\cdotp$\ \ \href{mailto:PBouchey@paraport.com}{PBouchey@paraport.com}}

\vspace{1em} % Extra space between major sections

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\spacedlowsmallcaps{Education}\vspace{1em}

\NewEntry{2014-2017}{Georgia Institute of Technology}

\Description{\MarginText{Masters of Computer Science} School of Computer Science \newline
  Specialization: \textit{Machine Learning}\newline
Description: Classes include Machine Learning, Reinforcement Learning, Computability Complexity and Algorithms. Was selected out of over two thousand students to participate in the first cohort of the OMSCS program.}

\NewEntry{2005-2008}{University of Washington, Seattle}

\Description{\MarginText{Bachelors of Science - ACMS} Double degree in ACMS (Applied and Computational Mathematical Sciences) and Economics. Study focused on quantitative methods in economics, including financial modeling as well as optimization theory. \newline \MarginText{Bachelors of Science - Economics} Advisors: \textit{Dr. John Sullivan} \newline}


\NewEntry{2003-2005}{Olympic College, Bremerton}

\Description{\MarginText{Associate of Arts and Science} 
Finished associates degree by the time of high school graduation through the Running Start program.}


\vspace{1em} % Extra space between major sections

%----------------------------------------------------------------------------------------
%	PUBLICATIONS
%----------------------------------------------------------------------------------------

\spacedlowsmallcaps{Publications}\vspace{1em}

\NewEntry{Expected October 2015}{Thoughtful Machine Learning - In Python}

\Description{\MarginText{O'Reilly} In the updated version of \textit{Thoughtful Machine Learning} we delve deeper into the subject of writing machine learning software well. We talk about the common pitfalls of machine learning projects including things like "pipeline jungles", entangled data, real world shifts and other problems. We systematically go through a few cases and algorithms. This version will be updated to be fully in Python.}

\NewEntry{October 2014}{Thoughtful Machine Learning}

\Description{\MarginText{O'Reilly}This book is about applying test-driven development (TDD) to machine learning algorithms. The point is to catch the problems that might sink a product when it's deployed. This practical guide goes through the principles of TDD and machine learning.}

\NewEntry{September 2012}{The Ultimate Guide to Hiring Developers}

\Description{\MarginText{Self Published}The Ultimate Guide to Hiring Developers is an eBook devoted to figuring out how to hire developers in a competitive market. It includes insights (using research data from a survey), as to what developers really want in a job and how to attract them. It also involves some tricks of the trade.}

%----------------------------------------------------------------------------------------

\vspace{1em} % Extra space between major sections

%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS
%----------------------------------------------------------------------------------------

\spacedlowsmallcaps{Skills}\vspace{1em}

\Description{\MarginText{Advanced}\textsc{Ruby}, \textsc{Python}, \textsc{R}, \textsc{SQL} (MySQL, and Postgres), \textsc{Elasticsearch}, Machine Learning and Operations Research, Statistics, \textsc{Redis}}

\Description{\MarginText{Intermediate} \textsc{Clojure}, \LaTeX, \textsc{Java}, DevOps (Vagrant, Chef, Docker), \textsc{Go}}

\Description{\MarginText{Basic} \textsc{Javascript}, \textsc{html}, \textsc{Spark}, \textsc{C}}

%------------------------------------------------

\vspace{1em} % Extra space between major sections

%----------------------------------------------------------------------------------------
%	OTHER INFORMATION
%----------------------------------------------------------------------------------------

\spacedlowsmallcaps{Other Information}\vspace{1em}

\Description{\MarginText{Awards} 2015\ \ $\cdotp$\ \ Advanced Communicator Bronze Award - Toastmasters International}
\vspace{-0.5em} % Negative vertical space to counteract the vertical space between every \Description command
\Description{2000\ \ $\cdotp$\ \ Eagle Scout Award -- Boy Scouts of America}


%------------------------------------------------

\vspace{1em}

\Description{\MarginText{Sample of Speeches}2015\ \ $\cdotp$\ \ Lessons Learned: Machine Learning and Technical Debt -- Data Day} 

\vspace{-0.5em} % Negative vertical space to counteract the vertical space between every \Description command

\Description{2014\ \ $\cdotp$\ \ Part of Speech Tagging with Hidden Markov Models -- Seattle.rb}

\vspace{-0.5em}

\Description{2014\ \ $\cdotp$\ \ Sentiment Analysis using Support Vector Machines -- MagmaConf MX}

\vspace{-0.5em}

\Description{2013\ \ $\cdotp$\ \ Test Driven Neural Networks with Ruby -- RubyConf Miami Florida}

\vspace{-0.5em}

\Description{2013\ \ $\cdotp$\ \ How to Overcome the apathy of Big Data -- Big Ruby Conf}

%------------------------------------------------

\vspace{1em}

\newlength{\langbox} % Create a new length for the length of languages to keep them equally spaced
\settowidth{\langbox}{English} % Length equals the length of "English" - if you have a longer language in your list put it here

\Description{\MarginText{Languages}\parbox{\langbox}{\textsc{English}}\ \ $\cdotp$\ \ \ Mothertongue}

\vspace{-0.5em} % Negative vertical space to counteract the vertical space between every \Description command

\Description{\parbox{\langbox}{\textsc{German}}\ \ $\cdotp$\ \ \ Intermediate}

\vspace{-0.5em} % Negative vertical space to counteract the vertical space between every \Description command

\Description{\parbox{\langbox}{\textsc{Vietnamese}}\ \ $\cdotp$\ \ \ Basic (simple words and phrases only)}

\vspace{1em} % Negative vertical space to counteract the vertical space between every \Description command

%------------------------------------------------

\Description{\MarginText{Interests}Piano\ \ $\cdotp$\ \ Woodworking\ \ $\cdotp$\ \ Triathlons\ \ $\cdotp$\ \ Hiking\ \ $\cdotp$\ \ Collecting Vinyl Records}

%----------------------------------------------------------------------------------------

\end{cv}

\end{document}
